Transcriptoinal symphony

### 2020-05-13 analysis/old/20_forrechelle.Rmd
moving old scripts like moved old figures

candidategenes <- c("PRLR", "PRL", "CISH", "JAK2", "SOCS3", "GH" )
datadrivengenes <- c("COX1", "PRL", "CHGA", "ATP2B4", "LOC107055658")

calisigenes <- c("PRL", "PRLR", 
                 "VIP", "VIPR1", "VIPR2", 
                 "OXT", "AVP", "AVPR1A", "AVPR1B", 
                 "GNRH1","GNRHR", "NPVF",
                 "NR3C1", "NR3C2",
                 "ESR1", "ESR2", "AR")

>>>>

candidategenes <- c("PRLR", "PRL", "CISH", "JAK2", "SOCS3", "GH", "FSHB", "CGA" )

datadrivengenes <- c("COX1", "PRL", "CHGA", "ATP2B4", "LOC107055658")

calisigenes <- c("PRL", "PRLR", 
                 "VIP", "VIPR1", "VIPR2", 
                 "OXT", "AVP", "AVPR1A", "AVPR1B", 
                 "GNRH1","GNRHR", "NPVF",
                 "NR3C1", "NR3C2",
                 "ESR1", "ESR2", "AR",
                 "FSH", "CGA")

### 2020-05-13 analysis/old/22_symphony.Rmd
moving old scripts like moved old figures

```{r setup, include=FALSE}
library(tidyverse)
library(ggimage)
library(cowplot)

source("../R/themes.R")

@@

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(ggimage)
library(cowplot)
library(ggsignif)

source("../R/themes.R")
source("../R/functions.R")
source("../R/wrangledata.R")

@@

```{r, fig.height=6}
head(candidatevsd)

candidatevsd %>%
  filter(gene == "PRL")  %>%
  ggplot(aes(x=treatment, y=counts)) + 
  geom_boxplot() +
  theme_B3() +
  geom_signif(comparisons = list(c("control", "bldg"),
                                 c( "bldg", "lay"),
                                 c( "lay", "inc.d3"),
                                 c("inc.d3", "inc.d9"),
                                 c( "inc.d9", "inc.d17"),
                                 c( "inc.d17", "hatch"),
                                 c("hatch", "n5"),
                                 c( "n5", "n9")),  map_signif_level=TRUE)  +
  facet_wrap(tissue~sex, scales = "free_y")
```
